EldersAIR: Main analysis - PM/Exposure Outcomes

### 2021-05-21 main_analysis_pm.Rmd
Minor updates for analysis/figures

---
title: 'EldersAIR: Main analysis - PM/Exposure Outcomes'
author: "Ethan Walker"
date: "Started 6 May 2021; Updated 12 May 2021"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) 
```

@@

itt_pm_results_primary <- lmer(log(outcome) ~ treatment + moisture_ave +
                                baseline_outcome + (1 | home:cohort:area), 
                                data = pm_data_2row)

@@

>>>>

---
title: 'EldersAIR: Main analysis - PM/Exposure Outcomes'
author: "Ethan Walker"
date: "Started 6 May 2021; Updated 18 May 2021"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds"))

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")
```

@@

itt_pm_results_primary <- lmer(log(outcome) ~ treatment + 
                                baseline_outcome + (1 | home:cohort:area), 
                                data = pm_data_2row)

@@

```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")

indoor_pm_boxplot <- analysis_data %>% 
  filter(!is.na(pm_mean_visit)) %>% 
  filter(!is.na(treatment)) %>% 
  mutate("Winter Sampling Period:" = factor(winter_id, levels = c(1, 2),
                                  labels = c("Baseline", "Post-Intervention"))) %>% 
  ggplot() + 
    geom_boxplot(aes(treatment, pm_mean_visit, fill = `Winter Sampling Period:`, size = 1), 
                 lwd = 1.2, colour = "black", 
                 fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(y = expression(paste("48-hour Mean Indoor PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme_minimal() +
    scale_y_log10() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9"))
indoor_pm_boxplot

#ggsave("elders_pm_boxplots.jpg", width = 8, height = 5)
```
